Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-12-03 prop_letter_ajhs.tex
prop_letter_ajhs.tex Copied from prop_letter_ajhs.tex...

\yutsung{Git Test!!!}

@@

We begin with the concept of $\delta$-determinism where~$\delta$
quantifies the effect of finite-precision uncertainties on measurement
outcomes. We recast the Kochen-Specker theorem using
$\delta$-determinism to quantify the effects of finite precision and
imperfections on contextuality. When $\delta=0$, the generalized
theorem reduces to the conventional one but as $\delta$ varies from 0
to 1 we note a transition from contextuality to non-contextuality.
% A principal result is that recasting the Kochen-Specker theorem in 
% terms of ``$\delta$-determinism,'' with~$\delta$ quantifying the 
% effect of finite-precision uncertainties on measurement outcomes, 
% reducing to the purely deterministic Kochen-Specker case for 
% $\delta=0$, can resolve the question of the effect of finite precision 
% and imperfections on contextuality.  
In more detail, the quantum-mechanical requirement for contextuality
continues to hold, thus maintaining the Kochen-Specker result for a
\emph{non-vanishing} range of $\delta$, but that at a \emph{certain
  fixed value} of $\delta$, there is a sharp transition, parallel in
its consequences to, say, a phase transition, to
\emph{non-contextuality}. %% ; that is, suddenly a quantum system can be
%% simulated by a non-contextual hidden variable theory.
%% , turning the
%% system effectively from a quantum system into a classical system. 
% that is, quantum mechanics suddenly fails to hold, and all variables
% can be specified simultaneously, turning the theory effectively into a
% classical theory that can be specified consistently by hidden
% variables.
% \yutsung{The part after ``that is''
%   looks strange.
% \begin{enumerate}
% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
% quantum mechanics can be simulated by a non-contextual deterministic hidden
% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
% doesn't make a lot sense.
% \item The question is whether there exist a QIVPM means ``a classical theory
% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
% I need to check whether it qualities as a classical probabilistic hidden variable
% theory\ldots(?)
% \end{enumerate}
% }
These results provide a new insight into the Meyer-Mermin debate by
presenting a theory in which there is a \emph{parameter} interpolating
between what appeared previously to be irreconcilable interpretations
of contextuality.

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule determining the probability of a given
measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
Here, Gleason's theorem establishes that there is no alternative to
the Born rule by demonstrating, using reasonable continuity arguments
in Hilbert spaces of dimension $d\ge3$, the existence of a unique
state $\rho$ consistent with the statistical predictions computed from
the Born rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Our question then concerns what happens when infinite precision cannot
be achieved.  We are able to show that, while a QIVPM incorporating
the effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert
space~$\Hilb$ of dimension $d\ge3$, there is a mathematically precise
sense in which one recovers the original Gleason theorem
asymptotically.  Specifically, it is possible to construct a class of
QIVPMs representing bounded resources that is parameterized by the
size of the intervals. We then demonstrate that all QIVPMs in this
class are consistent with a non-empty ``ball'' of quantum states whose
radius is defined by the maximal length of the
intervals characterizing the uncertainties. As the size of the intervals  
goes to zero, this ball of quantum states converges to a
point representing the unique state consistent with the Born rule and 
Gleason's theorem. 
%% We furthermore establish a mathematical correlation between the sizes
%% of the intervals and the volume of states that are all consistent with
%% an imprecise measurement.  \andy{``volume of states" are not defined
%%   in the Gleason's section.}

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain
events~\cite{Kolmogorov1950bibTeX,544199,Griffiths2003,Grabisch2016}. In the
quantum case, the events of interest are specified by \emph{projection
  operators} $P$ satisfying the condition $P^2=P$. These include the
empty projector~$\mathbb{0}$, the identity projector~$\mathbb{1}$,
projectors of the form $\proj{\phi}$ where $\ket{\phi}$ is a pure
quantum state (an element of a Hilbert space ${\cal H}$), sums of
\emph{orthogonal} projectors~$P_0$ and~$P_1$ with $P_0P_1=\mathbb{0}$,
and products of \emph{commuting} projectors $P_0$ and~$P_1$ with
$P_0P_1=P_1P_0$. In a quantum probability
space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012},
each event~$P_{i}$ is mapped to a probability~$\mu(P_{i})$ using a
probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$ is
the set of all events, projectors on a given Hilbert space, subject to the
following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}
Given a Hilbert space ${\cal H}$ of dimension $d$ and a probability assignment
for every projector $P$, we can define the expectation value of an
observable~$\mathbf{O}$ having spectral decomposition
$\mathbf{O}=\sum_{i=1}^{d}\lambda_{i}P_{i}$, with eigenvalues $\lambda_i \in
\mathbb{R}$, as~\cite{544199,Jaeger2007}:
\begin{equation}
\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{d}\lambda_{i}\mu(P_{i})\,.\label{eq:quantum-expectation}
\end{equation}

A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

The above axioms describe a mathematical idealization in which the
state of the quantum is known and involving infinitely precise
measurements. In an actual experimental setup with an ensemble of
quantum states whose states are unknown, that are not exactly
identically prepared, and with small imperfections and inaccuracies in
measuring devices, an experimenter might only be able to determine
that the probability of an event $P$ is concentrated in the range
$[0.49,0.51]$ instead of being precisely $0.5$. The spread in this
range depends on the amount of resources (time, energy, money, etc.)
that are devoted to the experiment. In the classical setting, this
``fuzziness'' can be formalized by moving to \emph{interval-valued
  probability measures} (IVPMs), which we explore in the next section,
along with our proposed extension to the quantum domain.

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$,
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. Under some additional assumptions, this
interval could be interpreted as the Gaussian width of a probability
distribution. We, however, use general intervals with no constraints
other than the ones needed to maintain coherence: these are described
next.

@@

We now show that our definition of QIVPMs is consistent with classical
IVPMs in the sense that a restriction of QIVPMs to mutually commuting
events recovers the definition of classical IVPMs. To formalize this
connection, we first note that in contrast to the case with
conventional quantum probability spaces, there is generally no unique
state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
is \emph{consistent} with a state $\rho$ and projector~$P$ if the
interval $\bar{\mu}(P)$ contains the exact probability calculated by
the Born rule, i.e, if:
\begin{equation}
\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)$
is the probability of the event~$P$ as determined by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

The proof that QIVPMs become classical IVPMs when the space of events
includes only mutually commuting events is presented in detail in a
forthcoming thesis~\cite{TaiThesis2018}. The idea of the proof is as
follows. Given a subspace of mutually commuting events~$\eventsC$, we
can construct a partial orthonormal basis by diagonalization and
complete it to a full orthonormal basis $\overline{\eventsC}$. We then
build a bijection between the QIVPM on the set of projectors
associated with this basis and the set of classical events
corresponding to this basis. Using this correspondence together with a
classical result by
Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
we can establish that for the special case of commuting events, a
QIVPM will always have a non-empty core~\footnote{Shapley's result
  proves that a classical IVPM always contains at least one state that
  is consistent with every event.}.

@@

The importance of this property is that it is violated in
finite-precision versions of Gleason's theorem
(cf. Thm.~\ref{thm:Non-extensible-of-Gleason's} in Sec.~\ref{sec:Gleason}). As we will show, the set of states
$\coreBorn\left(\bar{\mu},\events'\right)$ that is consistent with
some arbitrary (not necessarily commuting) events~$\events'$ and a
particular QIVPM $\bar{\mu}$ may be \emph{empty}.

@@

As is the case for conventional, infinitely-precise, quantum
probability measures, the theorem is only applicable to dimensions
$d \geq 3$. Indeed when the Hilbert space has dimension 2, it is
straightforward to construct a 0-deterministic QIVPM as
follows. Consider a non-contextual hidden variable model for $d=2$
(e.g., as proposed by Bell or
Kochen-Specker~\cite{BELL_1966,kochenspecker1967}). Such a
two-dimensional model assigns definite values to all observables at
all times, and hence assigns a \emph{determinate} probability (0 or 1)
to each event. This probability measure directly induces a
0-deterministic QIVPM by changing 0 to $\imposs$ and 1 to
$\necess$. The result follows is every 0-deterministic QIVPM is a
$\delta$-deterministic one.

@@

\begin{thm}[Empty Core for General
  QIVPMs]\label{thm:Non-extensible-of-Gleason's}There exists a Hilbert
  space and a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ such
  that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}

@@

\begin{tabular}{cc}
\toprule 
\addlinespace
$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, 
$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
\midrule 
\addlinespace
All other projectors & $\unknown$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Next we will prove by contradiction that
$\coreBorn\left(\bar{\mu},\events\right)$ is the empty set. Suppose
there is a state
$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j} > 0$. Since
we assumed the core is non-empty $\muB_{\rho}(P)\in\bar{\mu}(P)$, then
$\bar{\mu}(\proj{0})=\imposs=[0,0]$ from Table~\ref{tab:non-Born-QIVPM} requires
$\muB_{\rho}(P)=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
Therefore, $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all~$j$. The last equation never holds, proving the theorem.

@@

Thm.~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
theorem in the sense that it accounts for a larger class of probability measures that includes
the conventional one as a limit. The theorem is however ``special'' in
the sense that it only applies to the particular class of QIVPMs
constructed by composing a blurring function with a conventional
quantum probability measure. QIVPMs constructed in this manner have
some peculiar properties that we examine next.

@@

Statement~\ref{enu:iota-subject-to} implies \ref{enu:iota-mu-CIVPM}
and~\ref{enu:iota-mu-QIVPM} as we have outlined above. Conversely, for the quantum case, we want
to show that if $\ultramodular$ is not ultramodular, then for
some quantum probability measure $\mu$, the composite
$\ultramodular\circ\mu$ might not be a QIVPM. Suppose there are three
particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but they don't
satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider the state:
\[
\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-y\right)\proj{3}\,.
\]
The induced map using the Born rule and blurred by $\ultramodular$,
$\ultramodular\circ\muB_{\rho}$, fails to satisfy
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) when
$P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$. In other
words, this induced map fails to be a QIVPM. For the classical case, if
$\ultramodular$ is not ultramodular, we also want to find a classical
probability measure $\mu:\eventsC\rightarrow\left[0,1\right]$ such
that $\ultramodular\circ\mu$ is not a classical IVPM. This can be
done by restricting our previous quantum probability measure
$\muB_{\rho}$ to a commuting subspace of
event~$\eventsC$ generated by $\proj{0}$, $\proj{1}$, $\proj{2}$,
and $\proj{3}$. The restricted function
$\mu=\muB_{\rho}|_{\eventsC}$ is a classical probability
measure, and the induced map $\ultramodular\circ\mu$ fails to be
a classical IVPM for the same reason as the quantum case.

>>>>

%% ajh - SUGGESTED INTRO SENTENCE: TEXT #0 would go here.

@@

%% ajh "begin" doubled, replace here; two missing commas
We start our investigation with the concept of $\delta$-determinism, where~$\delta$
quantifies the effect of finite-precision uncertainties on measurement
outcomes. We recast the Kochen-Specker theorem using
$\delta$-determinism to quantify the effects of finite precision and
imperfections on contextuality. When $\delta=0$, the generalized
theorem reduces to the conventional one, but as $\delta$ varies from 0
to 1 we note a transition from contextuality to non-contextuality.
% A principal result is that recasting the Kochen-Specker theorem in 
% terms of ``$\delta$-determinism,'' with~$\delta$ quantifying the 
% effect of finite-precision uncertainties on measurement outcomes, 
% reducing to the purely deterministic Kochen-Specker case for 
% $\delta=0$, can resolve the question of the effect of finite precision 
% and imperfections on contextuality.  
%% ajh kill "In more detail"
%% ajh -  LONG SUGGESTED TEXT #1 would go here
The quantum-mechanical requirement for contextuality
continues to hold, thus maintaining the Kochen-Specker result for a
\emph{non-vanishing} range of $\delta$, but that at a \emph{certain
  fixed value} of $\delta$, there is a sharp transition, parallel in
its consequences to, say, a phase transition, to
\emph{non-contextuality}. %% ; that is, suddenly a quantum system can be
%% simulated by a non-contextual hidden variable theory.
%% , turning the
%% system effectively from a quantum system into a classical system. 
% that is, quantum mechanics suddenly fails to hold, and all variables
% can be specified simultaneously, turning the theory effectively into a
% classical theory that can be specified consistently by hidden
% variables.
% \yutsung{The part after ``that is''
%   looks strange.
% \begin{enumerate}
% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
% quantum mechanics can be simulated by a non-contextual deterministic hidden
% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
% doesn't make a lot sense.
% \item The question is whether there exist a QIVPM means ``a classical theory
% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
% I need to check whether it qualities as a classical probabilistic hidden variable
% theory\ldots(?)
% \end{enumerate}
% }
These results provide a new insight into the Meyer-Mermin debate by
presenting a theory in which there is a \emph{parameter} interpolating
between what appeared previously to be irreconcilable aspects %interpretations
of contextuality.
% ajh- above: I think "interpretations" is not quite right -> "aspects"?

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule determining the probability of a given
measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
Here, Gleason's theorem establishes that there is no alternative to
the Born rule by demonstrating, using reasonable continuity arguments
in Hilbert spaces of dimension $d\ge3$, the existence of a unique
state $\rho$ consistent with the statistical predictions computed from
the Born rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Our question then concerns what happens when infinite precision cannot
be achieved.  We are able to show that, while a QIVPM incorporating
the effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert
space~$\Hilb$ of dimension $d\ge3$, there is a mathematically precise
sense in which one recovers the original Gleason theorem
asymptotically.  Specifically, it is possible to construct a class of
QIVPMs representing bounded resources that is parameterized by the
size of the intervals. We then demonstrate that all QIVPMs in this
class are consistent with a non-empty ``ball'' of quantum states whose
radius is defined by the maximal length of the
intervals characterizing the uncertainties. As the size of the intervals  
goes to zero, this ball of quantum states converges to a
point representing the unique state consistent with the Born rule and 
Gleason's theorem. 
%% ajh: above starting at "We then demonstrate" LONG SUGGESTED TEXT #2
%% would go here: use PLURAL, ball -> balls, and then, to me, it would
%% be better as "..converges to a dense set of points."

%% We furthermore establish a mathematical correlation between the sizes
%% of the intervals and the volume of states that are all consistent with
%% an imprecise measurement.  \andy{``volume of states" are not defined
%%   in the Gleason's section.}

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain
events~\cite{Kolmogorov1950bibTeX,544199,Griffiths2003,Grabisch2016}. In the
quantum case, the events of interest are specified by \emph{projection
  operators} $P$ satisfying the condition $P^2=P$. These include the
empty projector~$\mathbb{0}$, the identity projector~$\mathbb{1}$,
projectors of the form $\proj{\phi}$ where $\ket{\phi}$ is a pure
quantum state (an element of a Hilbert space ${\cal H}$), sums of
\emph{orthogonal} projectors~$P_0$ and~$P_1$ with $P_0P_1=\mathbb{0}$,
and products of \emph{commuting} projectors $P_0$ and~$P_1$ with
$P_0P_1=P_1P_0$. In a quantum probability
space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012},
each event~$P_{i}$ is mapped to a probability~$\mu(P_{i})$ using a
probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$ is
the set of all events, (i.e., projectors on a given Hilbert space), %% ajh ()
subject to the 
following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}
Given a Hilbert space ${\cal H}$ of dimension $d$ and a probability assignment
for every projector $P$, we can define the expectation value of an
observable~$\mathbf{O}$ having spectral decomposition
$\mathbf{O}=\sum_{i=1}^{d}\lambda_{i}P_{i}$, with eigenvalues $\lambda_i \in
\mathbb{R}$, as~\cite{544199,Jaeger2007}:
\begin{equation}
\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{d}\lambda_{i}\mu(P_{i})\,.\label{eq:quantum-expectation}
\end{equation}

%% ajh: Inverted logic: LONG SUGGESTED TEXT #3 would go here
A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

%% ajh: big problems here: LONG SUGGESTED TEXT #5 would go here.  To
%% begin with, "axioms" is COMPLETELY undefined, appears NOWHERE in
%% the text except here.  So either NAME and LIST (instead of inline
%% text)  the several statements around Eq. (6) as axioms, or use
%% another term.  In addition the english "state of the quantum" is
%% wrong here.  Including fixing that, I would replace the first two
%% sentences by TEXT # 5.  It's really strangely written.
The above axioms describe a mathematical idealization in which the
%%state of the quantum is known and involving infinitely precise
quantum state is known and involving infinitely precise
measurements. In an actual experimental setup with an ensemble of
quantum states whose states are unknown, that are not exactly
identically prepared, and with small imperfections and inaccuracies in
measuring devices, an experimenter might only be able to determine
that the probability of an event $P$ is concentrated in the range
$[0.49,0.51]$ instead of being precisely $0.5$. The spread in this
range depends on the amount of resources (time, energy, money, etc.)
that are devoted to the experiment. In the classical setting, this
``fuzziness'' can be formalized by moving to \emph{interval-valued
  probability measures} (IVPMs), which we explore in the next section,
along with our proposed extension to the quantum domain.

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$,
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. Under some additional assumptions, this
interval could be interpreted as the Gaussian width of a probability
distribution. We, however, use general intervals with no constraints
other than the ones needed to maintain coherence: these are described
next.
%% ajh; previous sentence: I am aware of no previous definition of the
%% concept of "the constraints needed to maintain coherence" or what
%% that possibly means in definable sense. I do not know how to fix
%% it, or even if anyone else has trouble with this phrase as I did.

@@

%% ajh: inverted logic and phrasing.  I would start at "To formalize
%% this ..." and replace all the way to Eq (9) by LONG SUGGESTED TEXT
%% #6,  which coherently introduces the "core" and sets if off as a
%% DEFINITION, etc. 
We now show that our definition of QIVPMs is consistent with classical
IVPMs in the sense that a restriction of QIVPMs to mutually commuting
events recovers the definition of classical IVPMs. To formalize this
connection, we first note that in contrast to the case with
conventional quantum probability spaces, there is generally no unique
state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
is \emph{consistent} with a state $\rho$ and projector~$P$ if the
interval $\bar{\mu}(P)$ contains the exact probability calculated by
the Born rule, i.e, if:
\begin{equation}
\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)$
is the probability of the event~$P$ as determined by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

%%ajh: This story order is incomprehensible.  In my suggested
%% replacement: LONG SUGGESTED TEXT #7, I would state FIRST that 'here
%% is the outline of the proof', and LAST 'Thm 1..., whose full proof
%% will appear in [44].
The proof that QIVPMs become classical IVPMs when the space of events
includes only mutually commuting events is presented in detail in a
forthcoming thesis~\cite{TaiThesis2018}. The idea of the proof is as
follows. Given a subspace of mutually commuting events~$\eventsC$, we
can construct a partial orthonormal basis by diagonalization and
complete it to a full orthonormal basis $\overline{\eventsC}$. We then
build a bijection between the QIVPM on the set of projectors
associated with this basis and the set of classical events
corresponding to this basis. Using this correspondence together with a
classical result by
Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
we can establish that for the special case of commuting events, a
QIVPM will always have a non-empty core~\footnote{Shapley's result
  proves that a classical IVPM always contains at least one state that
  is consistent with every event.}.

@@

%% ajh - inverted narrative order, suggested fix in 
%%   LONG SUGGESTED TEXT #8 would go here
The importance of this property is that it is violated in
finite-precision versions of Gleason's theorem
(cf. Thm.~\ref{thm:Non-extensible-of-Gleason's} in Sec.~\ref{sec:Gleason}). As we will show, the set of states
$\coreBorn\left(\bar{\mu},\events'\right)$ that is consistent with
some arbitrary (not necessarily commuting) events~$\events'$ and a
particular QIVPM $\bar{\mu}$ may be \emph{empty}.

@@

As is the case for conventional, infinitely-precise, quantum
probability measures, the theorem is only applicable to dimensions
$d \geq 3$. Indeed when the Hilbert space has dimension 2, it is
straightforward to construct a 0-deterministic QIVPM as
follows. Consider a non-contextual hidden variable model for $d=2$
(e.g., as proposed by Bell or
Kochen-Specker~\cite{BELL_1966,kochenspecker1967}). Such a
two-dimensional model assigns definite values to all observables at
all times, and hence assigns a \emph{determinate} probability (0 or 1)
to each event. This probability measure directly induces a
0-deterministic QIVPM by changing 0 to $\imposs$ and 1 to
$\necess$.  It follows that every 0-deterministic QIVPM is
$\delta$-deterministic.
%% ajh: Fixed garbled sentence.

@@

\begin{thm}[Empty Cores Exist for General
  QIVPMs]\label{thm:Non-extensible-of-Gleason's}There exists a Hilbert
  space  ${\cal H}$ and a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ such
  that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}
%% ajh: fixed garbled statement, add ${\cal H}$

@@

\begin{tabular}{cc}
\toprule 
\addlinespace
$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, 
$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
\midrule 
\addlinespace
All other projectors & $\unknown$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Next we will prove by contradiction that
$\coreBorn\left(\bar{\mu},\events\right)$ is the empty set. Suppose
there is a state
$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j} > 0$. Since
we assumed the core $\coreBorn\left(\bar{\mu},\events\right)$ 
is non-empty, so  $\muB_{\rho}(P)\in\bar{\mu}(P)$, and 
Table~\ref{tab:non-Born-QIVPM} tells us that
$\bar{\mu}(\proj{0})=\imposs=[0,0]$, we must conclude that
$\muB_{\rho}(P)=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
If this is true, then $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all~$j$. The last equation never holds, proving the theorem.
%%ajh: garbled argument starting at 'Since we assumed', tried to fix.

@@

%% ajh: no abbreviations as first words of sentences.
Theorem~\ref{thm:Finite-precision-Gleason} generalizes Gleason's
theorem in the sense that it accounts for a larger class of probability measures that includes
the conventional one as a limit. The theorem is however ``special'' in
the sense that it only applies to the particular class of QIVPMs
constructed by composing a blurring function with a conventional
quantum probability measure. QIVPMs constructed in this manner have
some peculiar properties that we examine next.

@@

Statement~\ref{enu:iota-subject-to} implies \ref{enu:iota-mu-CIVPM}
and~\ref{enu:iota-mu-QIVPM} as we have outlined above. Conversely, for the quantum case, we want
to show that if $\ultramodular$ is not ultramodular, then for
some quantum probability measure $\mu$, the composite
$\ultramodular\circ\mu$ might not be a QIVPM. Suppose there are three
particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but they don't
satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider the state:
\[
\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-y\right)\proj{3}\,.
\]
The induced map using the Born rule and blurred by $\ultramodular$,
$\ultramodular\circ\muB_{\rho}$, fails to satisfy
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}) when
$P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$. In other
words, this induced map fails to be a QIVPM. For the classical case, if
$\ultramodular$ is not ultramodular, we also want to find a classical
probability measure $\mu:\eventsC\rightarrow\left[0,1\right]$ such
that $\ultramodular\circ\mu$ is not a classical IVPM. This can be
done by restricting our previous quantum probability measure
$\muB_{\rho}$ to the space of events  $\eventsC$  generated by the
mutually commuting projectors $\proj{0}$, $\proj{1}$, $\proj{2}$, and
$\proj{3}$.  The restricted function
$\mu=\muB_{\rho}|_{\eventsC}$ is then a classical probability
measure, and the induced map $\ultramodular\circ\mu$ fails to be
a classical IVPM for the same reason as in the quantum case.
%% ajh: sentence "This can be done..." is somehow garbled, tried to
%% fix.  $\eventsC$ is by DEFINITION a commuting subspace, so the
%% original sentence does not seem to have any meaning.  Are there
%% MORE mutually commuting projectors in $\eventsC$?  It would seem
%% that there are no others, so this is all confusing, as that would
%% make this sentence completely vacuous.
